Optimizing Structural Properties Of Neural Networks With Genetic Algorithms

### 2015-08-07 paper/paper.tex
abstract

\begin{abstract}
    In this article we examine how structural properties of neural
    networks, like the size or local synapse densities, affect their
    learning success for various tasks. To do so, we look at a rate based
    model for neural networks and apply the FORCE rule for the learning
    process. A sophisticated matching algorithm
    allows us to quantify the learning success of a network so that the
    fitness of structural characteristics, expressed by integer or
    floating-point parameters, can be evaluated. We then use evolutionary
    optimization methods on these parameters to show that (1) ring
    topologies are generally more successful than strictly random
    topologies, (2) *FAT
    LIST OF INCREDIBLE RESULTS THAT CHANGE THE UNIVERSE*
\end{abstract}

>>>>

\begin{abstract}
    In this article we examine how structural properties of neural
    networks, like the local synapse densities, affect their
    learning success for various tasks. To do so, we look at a rate based
    model for neural networks and apply a learning algorithm called FORCE to let the network learn 
		to reproduce either low or high frequent sinusoidals. A sophisticated matching algorithm
    allows us to quantify the learning success of a network so that the
    fitness of structural characteristics can be evaluated. We then use evolutionary
    optimization methods on these parameters, and found that for high frequencies, the
		$\feedback$ parameter can be increased  to improve learning results, at the cost of strongly 
		decreasing the ability to memorize low frequencies. Alternatively, using ring topology instead
		of random connections has a similar effect, but still retains the ability to learn lower frequencies.
\end{abstract}
